<<<<<<< HEAD
---
title: "Reproducible Research: Peer Assessment 1"
output: 
  md_document:
    variant: markdown_github
---

## Loading and preprocessing the data
```{r}
data <- read.csv("activity.csv")


```
## What is mean total number of steps taken per day?
```{r}
stepsdaily<-aggregate(steps~date, data, sum)
hist(stepsdaily$steps,breaks=25, col="red",  xlab="Number of Steps")

```

## What is the average daily activity pattern?
```{r}
steps_by_interval <- aggregate(steps ~ interval, data, mean)
stepsdaily <- aggregate(steps ~ date, data, sum)

plot(steps_by_interval$interval,steps_by_interval$steps, type="l", xlab="Interval", ylab="Number of Steps")
medsteps<-median(stepsdaily$steps)
meansteps<-mean(stepsdaily$steps)
max_interval <- steps_by_interval[which.max(steps_by_interval$steps),1]
```
The `mean` is `r meansteps` ; the `median` is `r medsteps` with an interval `maximum` interval of `r max_interval`


## Imputing missing values
```{r}
incomplete <- sum(is.na(data))
imputed_data <- transform(data, steps = ifelse(is.na(data$steps), steps_by_interval$steps[match(data$interval, steps_by_interval$interval)], data$steps))

```


```{r}
```

Recount total steps by day and create Histogram. 
```{r}
stepsdaily_i <- aggregate(steps ~ date, imputed_data, sum)
hist(stepsdaily_i$steps, breaks= 25, col="blue", xlab="Number of Steps")

#Create Histogram to show difference. 
hist(stepsdaily$steps, breaks=25, col="red", xlab="Number of Steps", add=T)
legend("topright", c("Imputed", "Non-imputed"), col=c("blue", "red"), lwd=10)
```

Calculate new mean and median for imputed data. 
```{r}
meansteps.i <- mean(stepsdaily_i$steps)
medsteps.i <- median(stepsdaily_i$steps)
```

Calculate difference between imputed and non-imputed data.
```{r}
mean_diff <- meansteps.i - meansteps
med_diff <- medsteps.i - medsteps
```

Calculate total difference.
```{r}
total_diff <- sum(stepsdaily_i$steps) - sum(stepsdaily$steps)
```
* The imputed data mean is `r meansteps.i`
* The imputed data median is `r medsteps.i`
* The difference between the non-imputed mean and imputed mean is `r mean_diff`
* The difference between the non-imputed median and imputed median is `r med_diff`
* By imputing with average amounts-- the median and mean remain the similar  
* The difference between total number of steps between imputed and non-imputed data is `r total_diff`. Thus, there were `r total_diff` more steps in the imputed data.

*However, a measure of kurtosis shows differences between the two distributions of data-- both have very large kurtosis values (data does not follow a normal distribution)
```{r}
library(e1071)
kurtosis(data$steps, na.rm=TRUE)
kurtosis(imputed_data$steps, na.rm=TRUE)
```

## Are there differences in activity patterns between weekdays and weekends?
Created a plot to compare and contrast number of steps between the week and weekend. There is a higher peak earlier on weekdays, and more overall activity on weekends.  
``` {r}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
imputed_data$dow = as.factor(ifelse(is.element(weekdays(as.Date(imputed_data$date)),weekdays), "Weekday", "Weekend"))

steps_by_interval_i <- aggregate(steps ~ interval + dow, imputed_data, mean)

library(lattice)

xyplot(steps_by_interval_i$steps ~ steps_by_interval_i$interval|steps_by_interval_i$dow, main="STEPS_BY_DAY",xlab="Interval", ylab="Steps",layout=c(1,2), type="l")

```