---
title: "Regression Coursera"
output:
  html_document: default
---
**Summary**
This project was done to explore the relationship between mileage in cars and transmission type (automatic vs manual)-- 
A simple model only looking at tramsission type finds a 7.25 MPG difference between the types of transmission (p < .05) 

R-squared for transission type only yields a low R-squared (.36).  Further analysis shows that there are other more significant contributors to MPG such as the weight of the car.  A more complete model (including weight, hp, cyl) changes the p-value of transmission type to no longer being significant (p=.3) but improves R-squared (.85) with only weight being significant at the .05 level.  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r mtcars}
fullmodel<-lm(mpg~ . , data=mtcars)
summary(fullmodel)
```
```{r}
ammod<-lm(mpg ~ am, data=mtcars)
summary(ammod)


```
R-squared is fairly low (.36), however, transission type is significant

```{r}
boxplot(mpg~am, data=mtcars, main= "Overall MPG by Type", names=c("automatic", "manual"))
```
at face value-- manual appears to have better MPG-- however, the average for automatic is contained within the error bars for automatic
```{r}
pairs(mpg ~ ., data = mtcars)
```
```{r}
mvr <- lm(mpg~am + wt + hp + cyl, data = mtcars)
summary(mvr)
anova(ammod,mvr)
```
A more Inclusive Model reduces the residual sum of squares significantly
```{r}
plot(mvr)
```
```{r}
plot(ammod)
```